Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-12 tex/VHzQ.tex
more tex/ edits, updates

\title[Very high-$z$ Quasars]
        {Near and Mid-infrared properties of known $z\geq5$ Quasars}
\author[Ross \& Cross]
       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
\\ 
$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
}

@@

@@

The science reach of $z>5$ quasars will continue to be important well into the next decade
\citep{Fan2019_DecadalWP, Wang2019_DecadalWP}
and will provide key insights into direct collapse black holes, hydrogen reionization and
the physics of accretion in the first $\lesssim$700 million years of the Universe.

>>>>

\title[Infrared properties Very high-$z$ Quasars]
  {Near and Mid-infrared properties of known $z\geq5$ Quasars}
\author[Ross \& Cross]
{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk} and Nicholas J. G. Cross\\ 
Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\ }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{SurfaceDensity}

@@

The science reach of $z>5$ quasars will continue to be important well
into the next decade \citep{Becker2019_DecadalWP, Fan2019_DecadalWP,
Wang2019_DecadalWP} and will provide key insights into direct collapse
black holes, hydrogen reionization and the physics of accretion in the
first $\lesssim$700 million years of the Universe.
